COG-ED Manuscript

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
pipelines are functional

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
                                           & (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))) | (pipelines_data[[i]]$level != x), ]

@@

              pipelines_data[[i]] <-
                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
                                           & (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))) | (pipelines_data[[i]]$level != x), ]
            }
        }

@@

              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]

@@

              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
            }
          }
        }

@@

              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]    
            } else if (pipeline_name[[1]][4] == "3") {

              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
            }
        }

>>>>

              ifelse(length(which(pipelines_data[[i]]$level == x &
                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x &
                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
                                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
        }

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

@@

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
          }
        }

@@

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
                                                      (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
        }
